BOUT

### 2023-08-25 Data & Scripts/BOUT.Rmd
Aug. 25

@@

sjPlot::tab_model(BOUT.MOD1
                  , show.re.var = T
                  , title = "Bout Model 1 Output"
                  , dv.labels = " Effects of on duration of bouts of behaviors")
```

@@

sjPlot::tab_model(BOUT.MOD2
                  , show.re.var = T
                  , title = "Bout Model 2 Output"
                  , dv.labels = " Effects of on duration of bouts of behaviors")
```

In the second model with the added interactions, the behavior, generalized environment and a number of interactions are significant. The interaction between behavior and generalized environment is significant, as well as the interaction between the presence of a sentinel and generalized environment. The interaction between behavior and group size is significant. Lastly, moving and bait presence were significant.

@@

sjPlot::tab_model(BOUT.MOD3
                  , show.re.var = T
                  , title = "Bout Model 3 Output"
                  , dv.labels = " Effects of on duration of bouts of behaviors")
```

@@

sjPlot::tab_model(BOUT.RMOD2
                  , show.re.var = T
                  , title = "Bout Robust Model 2 Output"
                  , dv.labels = " Effects on duration of bouts of behaviors")
```

>>>>

```{r Model Labels}
pl<-c(
  '(Intercept)' = "Intercept"
  , BEHAVIORHU = "Behavior"
  , SENTINEL_PRESENCEYES = "Sentinel Presence"
  , 'GENERALIZED_ENVIRONMENTGreen Area' = "Generalized Environment"
  , GROUP_SIZESMALL = "Group Size"
  , BAIT_PRESENCEYES = "Bait Presence"
  , DISTURBANCE_FREQUENCY = "Disturbance Frequency"
  , 'BEHAVIORHU:SENTINEL_PRESENCEYES' = "Behavior: Sentinel Presence"
  , 'BEHAVIORHU:GENERALIZED_ENVIRONMENTGreen Area' = "Behavior: Generalized Environment"
  , 'SENTINEL_PRESENCEYES:GENERALIZED_ENVIRONMENTGreen Area' = "Sentinel Presence: Generalized Environment"
  , 'BEHAVIORHU:SENTINEL_PRESENCEYES:GENERALIZED_ENVIRONMENTGreen Area' = "Behavior: Sentinel Presence: Generalized Environment"
)
```

@@

sjPlot::tab_model(BOUT.MOD1
                  , pred.labels = pl
                  , rm.terms = c("BEHAVIORM"
                                 ,"BEHAVIORM:SENTINEL_PRESENCEYES"
                                 , "BEHAVIORM:GENERALIZED_ENVIRONMENTGreen Area"
                                 ,"BEHAVIORM:SENTINEL_PRESENCEYES:GENERALIZED_ENVIRONMENTGreen Area")
                  , show.re.var = T
                  , title = "Bout Model 1 Output"
                  , dv.labels = " Effects of on duration of bouts of behaviors")
```

@@

sjPlot::tab_model(BOUT.MOD2
                  , pred.labels = pl
                  , rm.terms = c("BEHAVIORM"
                                 ,"BEHAVIORM:SENTINEL_PRESENCEYES"
                                 , "BEHAVIORM:GENERALIZED_ENVIRONMENTGreen Area"
                                 ,"BEHAVIORM:SENTINEL_PRESENCEYES:GENERALIZED_ENVIRONMENTGreen Area")
                  , show.re.var = T
                  , title = "Bout Model 2 Output"
                  , dv.labels = " Effects of on duration of bouts of behaviors")
```

In the second model with the added interactions, the behavior, generalized environment and a number of interactions are significant. The interaction between behavior and generalized environment is significant, as well as the interaction between the presence of a sentinel and generalized environment. The interaction between behavior and group size is significant. Lastly, moving and bait presence were significant (removed Moving from output).

@@

sjPlot::tab_model(BOUT.MOD3
                  , pred.labels = pl
                  , rm.terms = c("BEHAVIORM"
                                 ,"BEHAVIORM:SENTINEL_PRESENCEYES"
                                 , "BEHAVIORM:GENERALIZED_ENVIRONMENTGreen Area"
                                 ,"BEHAVIORM:SENTINEL_PRESENCEYES:GENERALIZED_ENVIRONMENTGreen Area")
                  , show.re.var = T
                  , title = "Bout Model 3 Output"
                  , dv.labels = " Effects of on duration of bouts of behaviors")
```

@@

sjPlot::tab_model(BOUT.RMOD2
                  , pred.labels = pl
                  , rm.terms = c("BEHAVIORM"
                                 ,"BEHAVIORM:SENTINEL_PRESENCEYES"
                                 , "BEHAVIORM:GENERALIZED_ENVIRONMENTGreen Area"
                                 ,"BEHAVIORM:SENTINEL_PRESENCEYES:GENERALIZED_ENVIRONMENTGreen Area")
                  , show.re.var = T
                  , title = "Bout Robust Model 2 Output"
                  , dv.labels = " Effects on duration of bouts of behaviors")
```
